Supporting Information : Asymmetric tail-dependence in extreme climatic events affects population-extinction risk

### 2019-08-29 SuppMat.Rmd
fig,results editting continued

```{r fig_agestr_mtd_linear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep., C","vital rates : RTdep., SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

```{r fig_agestr_mtd_nonlinear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep., C","vital rates : RTdep., SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep.","vital rates : RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep.","vital rates : RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

<!--Supp. FIG :  age structure model results for C, SC with linear model (\Omega = infinity)-->
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\caption[Extinction risk from single patch age structured models with time when vital rates have either left (C) or right tail (SC) dependence.]{Extinction risk (shading represents 95\% confidence interval) from single patch age structured models with time for 10000 simulations. Fecundity of adults and survival of eggs have moderate tail dependence in either left or right tail in their corresponding copula structure. Moderate left tail dependence (or right tail dependence) was generated by a bivariate Clayton (or Survival Clayton) copula with Kendall correlation coefficient = 0.6, $(A)$ for linear model ($\Omega = \infty$) and for $(B)$ non-linear model ($\Omega = 100$).\label{fig_extrisk_agestr_mtd}}
\end{center}
\end{figure}

<!--Supp. FIG :  summary : all nonlinear model results for global dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extremenoise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

>>>>

```{r fig_agestr_mtd_linear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: moderate LTdep.,C","vital rates: moderate RTdep.,SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2, seg.len = 1)
par(op)
dev.off()
```

@@

```{r fig_agestr_mtd_nonlinear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: moderate LTdep.,C","vital rates: moderate RTdep.,SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2, seg.len = 1)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: extreme LTdep.","vital rates: extreme RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: extreme LTdep.","vital rates: extreme RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2)
par(op)
dev.off()
```

@@

<!--FIG:  age structure model results for moderate tail dep. (C, SC)-->
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\caption[Extinction risk from single patch age structured models with time when vital rates have either left (C) or right tail (SC) dependence.]{Extinction risk (shading represents 95\% confidence interval) from single patch age structured models with time for 10000 simulations. Fecundity of adults and survival of eggs have moderate tail dependence in either left or right tail in their corresponding copula structure. Moderate left tail dependence (or right tail dependence) was generated by a bivariate Clayton (or Survival Clayton) copula with Kendall correlation coefficient = 0.6, $(A)$ for linear model ($\Omega = \infty$) and for $(B)$ non-linear model ($\Omega = 100$).\label{fig_extrisk_agestr_mtd}}
\end{center}
\end{figure}

<!--FIG:  summary: all nonlinear model results for local dispersion, moderate noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp_moderatenoise.pdf}
\caption[Analogous figure as that of Fig. \ref{MT-fig_extrisk_allmodel_localdisp_etd} in the maintext but with moderate tail dependence in spatially correlated noises.]{Analogous figure as that of Fig. \ref{MT-fig_extrisk_allmodel_localdisp_etd} in the maintext but with moderate tail dependence in spatially correlated noises.\label{fig_extrisk_allmodel_localdisp_mtd}}
\end{center}
\end{figure}

<!--FIG:  summary: all nonlinear model results for global dispersion, extreme noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extremenoise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--FIG:  summary: all nonlinear model results for global dispersion, moderate noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_moderatenoise.pdf}
\caption[Analogous figure as that of Fig. \ref{fig_extrisk_allmodel_globaldisp_mtd} but with moderate tail dependence in spatially correlated noises.]{Analogous figure as that of Fig. \ref{fig_extrisk_allmodel_globaldisp_mtd} but with moderate tail dependence in spatially correlated noises.\label{fig_extrisk_allmodel_globaldisp_mtd}}
\end{center}
\end{figure}

<!--FIG: Ricker model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8_etd}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6_etd}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6_etd}}
\end{center}
\end{figure}

======================
<!--FIG: Ricker model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of moderate tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of moderate tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1_mtd}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1_mtd}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8_mtd}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal, moderate noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1_mtd}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal, moderate noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6_mtd}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal, moderate noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_moderatenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6_mtd}}
\end{center}
\end{figure}
=========================

<!--FIG : Ricker model, global dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_global_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Hassell model, global dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_global_disp_scl_1_etd}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, global dispersal, extreme noise-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_global_disp_scl_0.8_etd}}
\end{center}
\end{figure}
